Approximate State Abstraction

### 2016-01-28 paper/paper.tex
Crappy proof that doesn't work for Lemma 1

{\bf Lemma 1:}
If the value of a state in the ground \ac{MDP} is within $\kappa \in \mathbb{R}$ of the value of the corresponding abstract state, then the value of the ground state under the optimal policy in the abstract \ac{MDP} is within $\kappa$ of the value of the ground state:
\begin{multline*}
| V_G(s) - V_A(\phi (s)) | \leq \kappa \rightarrow
\left| V_G(s) - V_G^{\pi_A^*} \right| \leq \kappa
\end{multline*}

\textbf{Proof:}

@@

Note that as $T \rightarrow \infty$, $V_T$ becomes $V^{\pi_A*}$. Therefore:

>>>>

{\bf Lemma 1:}
If the value of all states in the ground \ac{MDP} are within $\kappa \in \mathbb{R}$ of the value of their corresponding abstract state, then the value of all ground states under the optimal policy in the abstract \ac{MDP} are within $3 \kappa$ of the value of their corresponding ground states:
\begin{multline*}
\forall_{s\in \mathcal{S}_G} | V_G(s) - V_A(\phi (s)) | \leq \kappa \rightarrow\\
\forall_{s\in \mathcal{S}_G}\left| V_G(s) - V_G^{\pi_A^*}(s) \right| \leq 3\kappa
\end{multline*}

\textbf{Proof:}
Given a state, $s \in \mathcal{S}_G$ by definition:

Assume
\begin{equation}
\label{eq:similarValAssum}
|V_G(s) - V_A(\phi (s)) | \leq \kappa
\end{equation}

Let $s_A$ stand for $\phi(s)$

\begin{align*}
&V_A(s_A) = \max_a \left| R_A(s_A, a) + \gamma \sum_{s_A' \in \mathcal{S}_A} T_A(s_A, a, s_A') V_A(s'a)   \right| \\
&\leq \max_a \left| \sum_{g \in s_A} \left[ R_G(g,a) + \gamma  \sum_{g'}T_G(g, a, g')(V_g(g') + \kappa) \right] \right|\\
\end{align*}

\begin{equation}
\label{eq:similarValIntResult}
\leq \gamma \kappa + \sum_{g \in s_A} w(g)V_G(g)
\end{equation}

Given two ground states, $s_1$ and $s_2$ for which $\phi(s_1) = \phi(s_2)$ we know by Equation \ref{eq:similarValAssum} that 
\begin{align*}
V_A(\phi(s_1))-\kappa \leq V_G(s_1) \leq V_A(\phi(s_1))+\kappa
\end{align*}

and symmetrically that
\begin{align*}
V_A(\phi(s_1))-\kappa \leq V_G(s_2) \leq V_A(\phi(s_1))+\kappa
\end{align*}

By subtraction,
\begin{align*}
-2 \kappa \leq V_G(s_1) - V_G(s_2) \leq 2 \kappa \\
\end{align*}

\begin{equation}
\label{eq:similarValIntResult2}
\left|  V_G(s_1) - V_G(s_2) \right| \leq 2\kappa
\end{equation}

Let $g_{min}$ stand for $\underset{g}{argmin} V_{G}(g)$.

We know by equations \ref{eq:similarValIntResult} and \ref{eq:similarValIntResult2} that
\begin{align*}
V_A(s_A) &\leq \gamma \kappa +\sum_{g \in s_A} w(g)(V_G(g_{min})+2\kappa) \\
&\leq 3\kappa + V_G(g_{min})\\
V_A(s_A)  -  V_G(g_{min}) &\leq 3 \kappa
\end{align*}

@@

As $T \rightarrow \infty$, $V_T$ becomes $V^{\pi_A*}$. Therefore:
